Paper Report

### 2017-11-13 Paper_report.tex
Alignment model, NN in Word alignment model

%----------------------------------------------------------------------------------------
%	IBM models
%----------------------------------------------------------------------------------------

\section{IBM models}

@@

@@

\section{Overview about statistical alignment}
\subsection{General problem}
Input:
\begin{itemize}
\item A source sentence: $f_1^J = f_1,...,f_j,...f_J$
\item A target sentence: $e_1^I = f_1,...,f_i,...f_I$
\end{itemize}
Output: Alignment map $j \rightarrow i = a_j$
\begin{itemize}
\item An alignment: $a_1^J = a_1,...,a_j,...a_J$
\end{itemize}

\subsubsection{}
Our work is modelling the relationship between a source sentence and a target sentence. \\
We start from the view of translation model, which is finding this best translation $e_1^I$ for a source sentence $f_1^J$.
\begin{equation}
e_1^I = argmax_{e_1^I} p(e_1^I|f_1^J) = argmax_{e_1^I} \frac{p(f_1^J|e_1^I)p(e_1^I)}{p(f_1^J)}
\end{equation}

@@

\subsubsection{Problem of empty word}

@@

@@

>>>>

@@

\subsection{Result}

%----------------------------------------------------------------------------------------
%	Recurrent Neural Networks for Word Alignment Model
%----------------------------------------------------------------------------------------
\section{Recurrent Neural Networks for Word Alignment Model \citep{Tamura14recurrent}}

\subsection{Main idea}
This research is mainly based on \citep{Yang13word}. The difference is that the alignment score is calculated in recurrent approach RNNs, which means that $a_j$ depends on all previous position $a_{0...j-1}$.

\subsection{How does RNNs work in calculating alignment score ?}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

@@

\section{Overview about statistical alignment \cite{Och2003Systematic}}
\subsection{General problem}
Input:
\begin{itemize}
\item A source sentence: $f_1^J = f_1,...,f_j,...f_J$
\item A target sentence: $e_1^I = f_1,...,f_i,...f_I$
\end{itemize}
Output: Alignment map $j \rightarrow i = a_j$
\begin{itemize}
\item An alignment: $a_1^J = a_1,...,a_j,...a_J$
\end{itemize}

\subsubsection{How to model a word alignment ?}
Our work is modelling the relationship between a source sentence and a target sentence. \\
We start from the view of translation model, which is finding this best translation $e_1^I$ for a source sentence $f_1^J$.
\begin{equation}
e_1^I = argmax_{e_1^I} p(e_1^I|f_1^J) = argmax_{e_1^I} \frac{p(f_1^J|e_1^I)p(e_1^I)}{p(f_1^J)}
\end{equation}

@@

@@

\begin{equation}
p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
\label{AlignmentModelEquation}
\end{equation}

From this formula, we need to calculate these two components:
\begin{itemize}
\item $ p(f | e) $ : Translation probability
\item $p(a_j | a_{j-1}, I)$ or $p(i | i', I)$ : HMM alignment probability
\end{itemize}

\subsubsection{Assumption about HMM alignment probability $p(a_j | a_{j-1}, I)$ or $p(i | i', I)$}
Alignment probability depends on the difference in the alignment positions rather than on the absolute position \cite{Vogel1996HMM}.

\begin{equation}
p(i | i', I) = \frac{c(i - i')}{\sum_{i''=1}^I c(i'' - i')}
\end{equation}
where $c(i - i')$ is non-negative.

\subsubsection{Extension: Empty word in target sentence}
An source word could give an empty word, which is that each target word has an extra empty word. This leads to the length of target sentence being $e_{1}^{2I}$ and the empty word zone being $e_{I+1}^{2I}$. The word $e_{i}$ has an empty word $e_{i+I}$.

They enforce the constraints:
\begin{equation}
p(i + I | i', I) = p_{0} \delta(i, i')
\end{equation}
\begin{equation}
p(i + I | i' + I, I) = p_{0} \delta(i, i')
\end{equation}
\begin{equation}
p(i | i' + I, I) = p(i | i', I )
\end{equation}

where $p_{0}$ is the probability of a transition to the empty word.

\subsubsection{Extension: Refinement of alignment}

\begin{itemize}
\item Purpose: Add more assumptions that $p(a_j | a_{j-1}, I)$ depends on $e_{a_{j -1}}$ or $f_j$.
\item Problem: In the case of large corpora or large size of vocabulary, it leads to a large alignment parameters.
\item Solution: They use classes G which are the mappings of words to classes.
\end{itemize}

\section{Word alignment model in Neural Network}
We start from this formula \ref{AlignmentModelEquation}:

@@

In general, we try to calculate these probability by using two different neural networks.
The significant point of NN is Context.

\subsection{Non-probability approach, we use score}
The papers include \cite{Yang13word}, \cite{Tamura14recurrent}.
